\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
abstract
conclusion

We introduce a high-level SDN library that can be embedded into existing languages.
Our library exposes an API that allows programmers to directly express behavioral intent, 
while leaving the performance details to the library's optimization algorithms.
Our library supports basic tests on packet fields as well as a simple mutable table
data structure for storing global network information (e.g., firewall ACL, MAC learning table).
Finally, to ensure adequate performance, 
we statically analyze the programmer's policy by pushing symbolic packets through the policy 
and observing the resulting packet forwarding decision.

\end{abstract}

@@

\section*{Future Work and Conclusion}

>>>>

We introduce a high-level SDN library that can be embedded into existing languages.
Our library exposes an API that allows programmers to directly express behavioral intent, 
while leaving the performance details to the library's optimization algorithms.
Our library supports basic tests on packet fields as well as a simple mutable table
data structure for storing global network information (e.g., firewall ACL, MAC learning table).
Finally, to ensure adequate performance, 
we statically analyze the programmer's policy by pushing symbolic packets through the policy 
and observing the resulting packet forwarding decision.
\end{abstract}

@@

\section*{Future Work and Conclusion}
In this paper, we have introduced Oak, a SDN library for proactively switch forwarding rules
from an arbitrary programmer-defined policy in a general purpose programming language.
Oak provides programmers the abstraction that their centralized policy will run on each 
new packet entering the network, while alleviating for the programmer need to consider
how to split the decision logic between to switches and the controller.

The Oak API exposes simple tests on packet fields as well as a global, mutable table data
structure for recording information about previous packets observed in the network.
To ensure that most packets are handled directly on the switches, we employ a static analysis
that pushes symbolic packets through the programmer's policy to explore how all classes of 
packets will be handled, determining which packets must be observed by the controller and which 
packets need not be. Finally, we describe our Oak prototype's run-time system that 
specializes decisions after making concrete observations in the network that dictate forwarding policy.
